\documentclass[11pt]{article}

\title{Project Assessment}
\author{Hannah Eyre\\
	Zane Zakraisek}
\usepackage[margin=1.0in]{geometry}


\begin{document}
\maketitle



\begin{enumerate}

  \item What is your project about?
    \begin{itemize}
      \item \textit{Fake News} on Facebook.
        \begin{itemize}
          \item Links to content on external cites
          \item Public posts on large community pages
        \end{itemize}
      \item Using the different ethical frameworks discussed in class to find an appropriate level of moderation.
    \end{itemize}

  \item What is your plan for executing the project?
    \begin{itemize}
      \item The Annberg Public Policy Institute provides eight methods for identifying \textit{fake news}
        \begin{enumerate}
          \item Consider whether the source is credible.
          \item Read beyond the headline.
          \item Check whether the author is credible/real.
          \item Check whether the article is recent.
          \item Check whether it is a joke/satire.
          \item Consider your own biases and how they affect your judgment.
          \item Check supporting sources (if any) and make sure they abide by the same rules.
          \item Ask experts or fact-checking sites.
        \end{enumerate}
      \item Our plan is to examine these on a point by point basis using different ethical frameworks.
      \item We then plan to conclude whether or not it is ethical for Facebook to use these different methods on a case by case basis.
      \item Finally, we can use these individual conclusions to help us form a broad conclusion on Facebook's moderation in general.
    \end{itemize}

  \item How far have you gotten? 
    \begin{itemize}
      \item We've narrowed the project down using a few particular case studies.
        \begin{itemize}
          \item Pizzagate: example of possible consequences of unmoderated \textit{fake news}.
          \item Las Vegas shooting: This is a great example of how easily news sources and trending topics can be intentionally manipulated.
        \end{itemize}
    \end{itemize}

  \item What feedback would you like?
    \begin{itemize}
      \item Is it better to write about Facebook's moderation in overall, or should we have a conclusion with regards to each of the eight points?
      \item Should we focus specifically on data science (such as discussing acceptable error rates or the current feasibility of developing and implementing automated moderation or moderation tools) or should we also discuss methods that require primarily human intervention?
    \end{itemize}

\end{enumerate}



\end{document}
